On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-11-25 paper.tex
Rewriting

\affil[1]{\small Universidad Polit\'ecnica de Madrid. \texttt{luis.mendo@upm.es}}
%Information Processing and Telecommunications Center, Universidad Polit\'ecnica de Madrid\\
%Avenida Complutense, 30. 28040 Madrid, Spain.\\
\affil[2]{\small \texttt{arkhipov@alum.mit.edu}}

@@

The pair $(\isolr, \jsolr)$ can be obtained as a solution of the equation system
\begin{align}
\label{eq: icont jcont 1}
(\isolr-2)^2 a^2 + (\jsolr-2)^2 b^2 &= \len^2, \\
\label{eq: icont jcont 2}
\jsolr = \frac{\isolr a^2}{b^2} - \frac{5a^2}{2b^2} + \frac 3 2.
\end{align}
Substituting \eqref{eq: icont jcont 2} into \eqref{eq: icont jcont 1} yields a quadratic equation for $\isolr$,
\begin{equation}
\label{eq: quadratic, i}
4a^2(\isolr-2)^2 - 4a^2(\isolr-2) + a^2+b^2-\frac{4\len^2 b^2}{a^2+b^2} = 0,
\end{equation}
which can have zero, one or two real-valued solutions. These cases respectively mean that the solid line in Figure~\ref{fig: ijLS_1p35_detail} is exterior, tangent or secant to the circle (the figure shows the latter case). Only the solution with $\isolr, \jsolr \geq 2$, if any, is of interest. This solution can only exist as the one with largest $\isolr$ value when there are real-valued solutions, and it is obtained as %***Here rewriting
\begin{equation}
\label{eq: icont jcont 3}
\isolr = \frac{a + b \sqrt{4\len^2/(a^2+b^2)-1}}{2a} + 2.
\end{equation}

>>>>

\affil[1]{\small Universidad Polit\'ecnica de Madrid. E-mail:  \texttt{luis.mendo@upm.es}}
%Information Processing and Telecommunications Center, Universidad Polit\'ecnica de Madrid\\
%Avenida Complutense, 30. 28040 Madrid, Spain.\\
\affil[2]{\small E-mail: \texttt{arkhipov@alum.mit.edu}}

@@

The pair $(\isolr, \jsolr)$ can be obtained as a solution of the equation system
\begin{align}
\label{eq: icont jcont 1}
(\isolr-2)^2 a^2 + (\jsolr-2)^2 b^2 &= \len^2, \\
\label{eq: icont jcont 2}
\jsolr = \frac{\isolr a^2}{b^2} - \frac{5a^2}{2b^2} + \frac 3 2.
\end{align}
Substituting \eqref{eq: icont jcont 2} into \eqref{eq: icont jcont 1} yields a quadratic equation for $\isolr$,
\begin{equation}
\label{eq: quadratic, i}
4a^2(\isolr-2)^2 - 4a^2(\isolr-2) + a^2+b^2-\frac{4\len^2 b^2}{a^2+b^2} = 0,
\end{equation}
which can have zero, one or two real-valued solutions. These cases respectively mean that the solid line in Figure~\ref{fig: ijLS_1p35_detail} is exterior, tangent or secant to the circle (the figure shows the latter case). Only the solution with $\isolr, \jsolr \geq 2$, if any, is of interest. This solution can only exist as the one with largest $\isolr$ value when there are real-valued solutions, and it is obtained as %***Here rewriting. Maybe rephrase the following: the expression is general (isn't it?), i.e. may give complex values; and the three cases (0, 1 or 2 real solutions are not clearly identified) 
\begin{equation}
\label{eq: icont jcont 3}
\isolr = \frac{a + b \sqrt{4\len^2/(a^2+b^2)-1}}{2a} + 2.
\end{equation}
